\renewcommand{\theenumi}{\Alph{enumi}}

\chapter{Problem Statement}
\label{sec:ProblemStatement}

Explain the scope of your work, what will and will not be included. Is it
obvious where introductory material ("old stuff") ends and your contribution
("new stuff") begins? You should organize this section by idea, and not by
author or by publication. This section has tree main parts:

\begin{enumerate}
  \item a concise statement of the question that your thesis tackles
  \item justification, by direct reference to chapter
  \ref{sec:ReviewOfTheStateOfTheArt}, that your question is previously
  unanswered
  \item discussion of why it is worthwhile to answer this question.
\end{enumerate}

\section{Requirements}

\label{sec:Requirements}

\begin{enumerate}[label=\bfseries Goal:]%\arabic*:]
  \item The goal is a system with a flying component that is able get to a accident in a remote location and provide pictures.
\end{enumerate}

\begin{enumerate}[label=\bfseries D \arabic*:]
  \item The user of the system shall be able to control the flying component.
  \item The user shall be able to take pictures remotely.
  \item The user shall see the picture taken remotely in real time.
  \item The system must not force the user to move his location.
\end{enumerate}

\begin{enumerate}[label=\bfseries F \arabic*:]
  %\setcounter{enumi}{4}
  \item The user shall enter the coordinates into the ground station to which the flying component should fly.
  \item The system should find the fastest way to the operation area.
  \item The system shall be aware of the ground elevation in the operation range.
  \item The system shall provide a 360° view of the accident.
  \item The flying component should be controllable by a direct manual controller.
  \item The ground station shall provide a map with the flying component’s current location.
  \item The ground station shall provide the battery status of the flying component.
  \item The ground station shall provide the battery status of the flying component.
  \item The ground station shall indicate how much time is left before the flying component’s energy source will not allow the return flight any more.
  \item The flying component shall be able to recover from control signal loss.
  \item The flying component shall be able to return to a previously specified location and land in case of failure.
  \item The flying component shall take off and land autonomously.
  \item The system should allow real time video streaming from the remote location.
  \item The system should allow real time audio streaming from the remote location.
\end{enumerate}

\begin{enumerate}[label=\bfseries Q \arabic*:]
  %\setcounter{enumi}{4}
  \item The flying component shall take less than 5 minutes to fly 5 km with an altitude difference of 500m.
  \item The system's ground station shall be implemented as software.
  \item The ground station shall run on at least one out of Linux and Windows.
  \item The flying component shall be powered/recharged by electric current.
  \item Real time shall be less than 1 seconds for control commands.
  \item Real time shall be less than 2 seconds for pictures.
  \item Real time should be less than 1 second for streaming.
  \item The operating range shall be more then 10 km at 200 m over sea level.
  \item Pictures taken by the flying component shall have at least 2 MPx.
  \item The system shall be soft real time.
  \item System maintenance must not exceed 2 days per year
\end{enumerate}